---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(warn=-1)
```

# tidygeoRSS 🌎 🌍 🌏

![R-CMD-check](https://github.com/RobertMyles/tidygeoRSS/workflows/R-CMD-check/badge.svg)

The idea of tidygeoRSS is to parse 'geo' feeds -- RSS, Atom and JSON -- and return them as tibbles complete with the geographical information in a way that is compatible with the [sf](https://r-spatial.github.io/sf/articles/sf1.html) library. 

For more information on these formats, see: 

- geoRSS & geoAtom: [http://www.georss.org/](http://www.georss.org/)  
- geoJSON: [https://geojson.org/](https://geojson.org/)

## Installation

You can install the released version of tidygeoRSS from [CRAN](https://CRAN.R-project.org) with:

``` {r eval = FALSE}
install.packages("tidygeoRSS")
```

And the development version from [GitHub](https://github.com/RobertMyles/tidygeoRSS) with:

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("RobertMyles/tidygeoRSS")
```

### Installing sf

tidygeoRSS relies on sf, which also relies on some system dependencies, so you will most likely have to install certain things before using tidygeoRSS. More information is available [here](https://r-spatial.github.io/sf/index.html#installing). 

## Usage

### geoJSON example
```{r}
library(tidygeoRSS)
tidygeo("https://earthquake.usgs.gov/earthquakes/feed/v1.0/summary/2.5_day.geojson")
```

### geo-Atom example

```{r}
tidygeo("https://earthquake.usgs.gov/earthquakes/feed/v1.0/summary/all_hour.atom")
```

### geoRSS example

```{r}
tidygeo("http://www.geograph.org.uk/syndicator.php?format=GeoRSS")
```

